%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\renewcommand{\labelitemi}{--} % Changes the first-level bullet to a dash
% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item[--]\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Aneesh Iyer} \\ \vspace{1pt}
    \small \faPhone\ (513) 399-1607 $|$ \href{mailto:aiyer@gatech.edu}{\underline{\faEnvelope\ aiyer@gatech.edu}} $|$ 
    \href{https://linkedin.com/in/aneesh-iyer}{\underline{\faLinkedin\ in/aneesh-iyer}} $|$
    \href{https://github.com/aneesh-iyer29}{\underline{\faGithub\ github.com/aneesh-iyer29}} $|$ \href{https://aneesh-iyer29.github.io/}{\underline{\faGlobe\ aneesh-iyer29.github.io}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{May 2028}
      {B.S in Computer Engineering}{Atlanta, GA}
      \begin{itemize}[label=--]
          \item Cumulative GPA: 4.0
          \item Relevant Coursework: Linear Algebra, Calculus III, Ordinary Differential Equations, Physics I and II, Data Structures and Algorithms, Circuit Analysis, Low Level Programming
      \end{itemize}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, Rust, C, C++, SQL, JavaScript, HTML/CSS, R, MatLab, \LaTeX, Bash, Arduino, RISC-V} \\
     \textbf{Engineering Focus}{: Control Systems, Sensor Fusion, Embedded Systems, Systems Engineering, Aerospace Systems} \\
     \\
     \textbf{Proficiencies}{: Microsoft 365, Data Analytics, Modeling \& Simulation, Management, Teaching, Spanish (Intermediate)}
     \textbf{Interests}{: Machine Learning, Optics, Artificial Intelligence, Cryptography, Cybersecurity, Algorithms}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Engineer}{Sep. 2025 -- Present}
      {Architect Labs (prev. Nuntius YC 'S25)}{Remote}
      \resumeItemListStart
        \resumeItem{Designed and implemented custom data-based environments with synthetic data generation, automatic evaluation, and a custom reward system to quantify LLM model alignment in tool-based systems.}
        \resumeItem{Conducted penetration testing and failure analysis on AI models, uncovering security weaknesses and edge cases that informed model hardening strategies.}
    \resumeItemListEnd

    \resumeSubheading
      {Propulsive Landers}{Jan. 2026 -- Present}
      {Guidance, Navigation, and Control | Python, Rust}{Atlanta, GA}
      \resumeItemListStart
        \resumeItem{Developed control systems simulations for autonomous flight, implementing servo command scheduling to simulate time-dependent actuation in flight}
        \resumeItem{Implemented real-time sensor fusion using an Extended Kalman Filter and dynamic state transitions for estimation under noisy sensor conditions}

      \resumeItemListEnd

      
    \resumeSubheading
      {Experimental Physics Lab Assistant}{Aug. 2024 -- Dec. 2024}
      {State University of New York}{Remote}
      \resumeItemListStart
        \resumeItem{Processed and visualized real-time sensor data, applying statistical and graphical analysis methods }
        \resumeItem{Provided reference data and adjustments to enhance the quality and comprehensibility of the lab experience}

      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

      \resumeSubheading
      {Science Olympiad}{Aug. 2019 -- Present}
      {Captain, Competitor, Director}{Mason, OH \& Atlanta, GA}
      \resumeItemListStart
        \resumeItem{Led 3rd place National team; managed 100+ members, and oversaw resource exchange with 100+ schools.}
        \resumeItem{Directed a nationwide, 270-team tournament; raised \$20K, managed all logistics, communications, and awards.}
        \resumeItem{Notable Awards: 1st at Nationals in Optics, 2nd in Codebusters; 1st at MIT in Bungee Drop and Optics}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Mathworks Math Modeling (M3) Champion} $|$ \emph{Python, R}}{Mar. 2025 -- May 2025}
          \resumeItemListStart
            \resumeItem{Developed mathematical models to predict energy demand in Memphis in 2025 and 2045; validated models with real-world data using Python and SciPy}
            \resumeItem{Built multiple linear regression models with backward variable selection to quantify vulnerability, guiding targeted resource allocation based on statistical and socioeconomic indicators}
            \resumeItem{Presented findings live to Ph.D mathematicians; Published in the SIAM Undergraduate Research Online journal}
            \resumeItem{Placed 1st out of 794 teams internationally in the US and UK; Awarded \$20,000 grand prize}
            \resumeItem{Shao, Raymond, et al. “Hot Button Issue: Staying Cool as the World Heats Up.” \textit{SIAM Undergraduate Research Online}, vol. 18, 2025. Crossref, doi:10.1137/25s1777554.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{ScioVirtual Codebusters} $|$ \emph{HTML, CSS, Javascript}}{July 2024, 2025}
          \resumeItemListStart
            \resumeItem{Designed and developed an interactive Codebusters practice embed to solve questions for ScioVirtual.}
            \resumeItem{Created a dynamic UI allowing 70+ students to solve problems in real time and receive instant feedback}
            \resumeItem{Enhanced student engagement and hands-on learning experience, contributing to higher retention}
            \resumeItem{Recognized with “Instructor of the Year” award and the highest-rated class on the platform}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
    

%


%-------------------------------------------
\end{document}
